Approximation as Differentiation

### 2025-05-05 appendix/notes/auto-diff.tex
Spelling out auto-diff via Grothendieck.

>>>>

Let $X, Y, Z$ range over sets and $U, V, W$ range over finite vector spaces. Recall that the category
$\Fam(\FinVect) = \Grothendieck{}\Fam(-, \FinVect)$ (\defref{grothendieck:Grothendieck}) has:
\begin{itemize}
\item as objects, all pairs $(X, \{V_x\}_{x \in X})$ of a set $X$ and an object of $\Fam(X,\FinVect)$;
\item as morphisms $(X, \{V_x\}_{x \in X}) \to (Y, \{W_y\}_{y \in Y})$, all pairs $(f, \partial f)$ of
functions $f: X \to Y$ and families of morphisms $\partial f_x: \{V_x\}_{x \in X} \to \{W_{f(x)}\}_{x \in X}$
in $\Fam(X,\FinVect)$.
\end{itemize}

For any $(f, \partial f): (X, \{V_x\}_{x \in X}) \to (Y, \{W_y\}_{y \in Y})$ and $(g, \partial g): (Y,
\{W_y\}_{y \in Y}) \to (Z, \{U_z\}_{z \in Z})$ we have:
\begin{itemize}
\item $\partial f: \{V_x\}_{x \in X} \to \{W_{f(x)}\}_{x \in X}$;
\item $\Fam(g, \FinVect)(\partial g): \Fam(g, \FinVect)(\{W_y\}_{y \in Y}) \to \Fam(g, \FinVect)(\{Z_{g(y)}\}_{y \in Y})$.
\end{itemize}

### 2025-05-05 appendix/notes/fam.tex
Spelling out auto-diff via Grothendieck.

\begin{definition}[Category of $I$-indexed families of objects]
For any set $I$ and any category $\cat{C}$ write $\Fam(I,\cat{C})$ for the category which has:
\begin{itemize}
\item as objects all $I$-indexed families of objects of $\cat{C}$;
\item as morphisms from $X$ to $Y$ all families of morphisms $f_i: X_i \to Y_i$ in $\cat{C}$ for any $i \in
I$.
\end{itemize}
\end{definition}

>>>>

\begin{definition}[Category of $I$-indexed families of objects]
\label{def:fam:Fam}
For any set $I$ and any category $\cat{C}$ write $\Fam(I,\cat{C})$ for the category which has:
\begin{itemize}
\item as objects all $I$-indexed families of objects of $\cat{C}$;
\item as morphisms from $X$ to $Y$ all families of morphisms $f_i: X_i \to Y_i$ in $\cat{C}$ for any $i \in
I$.
\end{itemize}
\end{definition}
